Pre-registration

### 2020-03-21 docs/paper.rmd
update - still bugs to fix website

---
title: "Perceptions and Preferences for Meritocracy Scale (PPM-S)"
linestretch: '1.5'
link-citations: yes
output:
  html_document:
    number_sections: true
    toc: true
    toc_float: true
linkcolor: blue
bibliography: "../input/bib/EconomiaMoral.bib"
css: "../input/bib/style.css"

>>>>

---
title: "Perceptions and Preferences for Meritocracy Scale (PPM-S)"
linestretch: '1.5'
link-citations: yes
output:
  html_document:
    number_sections: true
    toc: true
    toc_float: true
linkcolor: blue
bibliography: "../input/bib/EconomiaMoral.bib"
# css: "../input/bib/style.css"

### 2020-03-21 docs/preanalisis.Rmd
update - still bugs to fix website

---
title: "Perceptions and Preferences for Meritocracy Scale (PPM-S)"
csl: "../input/bib/apa6.csl"
bibliography: "../input/bib/zlibrary.bib"
css: "../input/bib/style.css"
output:
  pdf_document:
    keep_tex: false
    template: null
    number_sections: true
    toc: true
  html_document:
    number_sections: true
    toc: true
    toc_float: true
geometry: margin=0.78in
header-includes:
  # - \usepackage[spanish,es-tabla,es-nodecimaldot]{babel}
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
linestretch: '1.5'
link-citations: yes
linkcolor: blue
---

@@

#Function to add the Figure Number
capFig = function(x){
  if(outputFormat == 'html'){
    x = paste0("**","Figura ",capFigNo,": ","**",x)
    capFigNo <<- capFigNo + 1
  }; x
}
```

@@

tab01 <- read.csv(file = "../input/data/original/materials/table01.csv",header = 1,sep = ";")

cnames <- c("Dimension", "Factor","Statement (english)" , "Statement (spanish)")

caption01 <- capTab("Meritocracy perception and preference")
kable(tab01,format = table_format,booktabs = T, linesep = "",col.names = cnames, caption = caption01) %>%
  kable_styling(full_width = T,latex_options = c("hold_position","scale_down"),position = "center",font_size = 9) %>%
  column_spec(column = 1,width = "1.5cm",) %>%
  column_spec(column = 2,width = "2 cm") %>%
  collapse_rows(columns = 1:2,valign = "middle")

>>>>

---
title: "Pre-registration"
csl: "../input/bib/apa6.csl"
bibliography: "../input/bib/zlibrary.bib"
# css: "../input/bib/style.css"
output:
  pdf_document:
    keep_tex: false
    template: null
    number_sections: true
    toc: true
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    smart: false
geometry: margin=0.78in
header-includes:
  # - \usepackage[spanish,es-tabla,es-nodecimaldot]{babel}
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
linestretch: '1.5'
link-citations: yes
linkcolor: blue
---

@@

#Function to add the Figure Number
capFig = function(x){
  if(outputFormat == 'html'){
    x = paste0("**","Figura ",capFigNo,": ","**",x)
    capFigNo <<- capFigNo + 1
  }; x
}
```
# Perceptions and Preferences for Meritocracy Scale (PPM-S)

(link to [PDF file](docs/preanalisis.pdf))

@@

# tab01 <- read.csv(file = "input/data/original/materials/table01.csv",header = 1,sep = ";")
#
# cnames <- c("Dimension", "Factor","Statement (english)" , "Statement (spanish)")
#
# caption01 <- capTab("Meritocracy perception and preference")
# kable(tab01,format = table_format,booktabs = T, linesep = "",col.names = cnames, caption = caption01) %>%
#   kable_styling(full_width = T,latex_options = c("hold_position","scale_down"),position = "center",font_size = 9) %>%
#   column_spec(column = 1,width = "1.5cm",) %>%
#   column_spec(column = 2,width = "2 cm") %>%
#   collapse_rows(columns = 1:2,valign = "middle")
